### 2014-12-10 ms/ms.Rmd
Update landing page. Closes #68

BAAD contains the following files:

- `dictionary.csv`: a table of variable definitions
- `data.csv`: amalgamated dataset, with columns as defined in `dictionary.csv`
- `references.bib`: bibtex entries containing the primary source for each study
- `references.csv`: summary of bibtex file, giving DOI, URL and citation of  the primary source for each study
- `contacts.csv`: list of contacts and affiliations for each study

>>>>

BAAD contains the following elements:

- `data`: amalgamated dataset, with columns as defined in `dictionary`
- `dictionary`: a table of variable definitions
- `metadata`: a table with columns "studyName","Topic","Description", containing written information about the methods used to collect the data
- `methods`: a table with columns as in data, but containing a code for the methods used to collect the data. See [config/methodsDefinitions.csv](config/methodsDefinitions.csv) for codes.
- `references`:  as both summary table (giving DOI, URL, citation) and bibtex entries containing the primary source for each study
- `contacts`: table with contacts and affiliations for each study.

These elements are available as both

1) a list within the file `baad.rds` (for use in R)
2) as a series of csv and text files.
